Vibrations and Heat Diffusion on the Unit Disc

### 2020-04-17 writeup/draft2.tex
minor edits

Partial differential equations (PDEs) are a natural extension to  ordinary differential equations, in that they describe systems that can vary with respect to multiple variables, traditionally position and time. Two fundamental PDEs are the heat and wave equations. Both of these involve the Laplace operator defined in the following way:

@@

    \lapl\psi+k^2\psi=0

@@

@@

>>>>

Partial differential equations (PDEs) are a natural extension to  ordinary differential equations, in that they describe systems that can vary with respect to multiple variables, traditionally position and time. Two fundamental PDEs are the heat and wave equations. Both of these involve the Laplace operator, defined in the following way:

@@

    \lapl\psi+k^2\psi=0\\

@@

Again the time component can be easily solved, to give the following solution:
  \chi_{\mathrm{wave}}=A\cos(kt)+B\sin(kt)
It is important to notice that for both of these equations, the spacial part is the same. Given that we are using the same boundary conditions for both equations, solving this equation will provide us with solutions to both the wave and heat equation.

@@

The above differential equation:
  \lapl \psi+k^2\psi=0
is known as the Helmholtz equation, and it describes the eigenvalues and eigenfunctions of the Laplacian on the unit disc. Recall that an eigenvalue equation is one where:
  \mc{L}v = \lambda v
where $\mc{L}$ is a linear operator, $v$ is an eigenvector, and $\lambda$ is an eigenvalue. In the context of differential operators, the eigenvectors are referred to as eigenfunctions.\\
Given our boundary data, the eigenfunctions will be ones that satisfy the following equations:
      \lapl \psi+k^2\psi=0 \\ 
      \psi(1,\phi) = 0
